Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-25 doc/JFLA2022/paper.tex
paper background outline

>>>>

\subsection{Background}

\begin{itemize}
\item formalizations of mathematics in proof assistants, such as Coq, continually grow in size and scope
\begin{itemize}
\item the Mathematical Components library and the four-color theorem and the odd order theorem in Coq
\item the Mathlib library for Lean
\end{itemize}
\item to continue to be useful as examples and reusable libraries, formalizations must be well \emph{documented} and \emph{maintained} to ensure they work with new proof assistant releases
\item Lean and Mathematical Components have accompanying books, which are written mainly to onboard new library users
\item book authors faced with several design choices: literate documents, using tools to keep the book and the proof assistant synchronized
\end{itemize}
